---
title: "task3"
author: "Logan Kozal"
date: "3/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(here)
library(tidyverse)
library(boot)
```

Data: 2014 UCSB Campus Climate Project Final Report (prepared by Rankin & Associates Consulting, available at http://campusclimate.ucop.edu/_common/files/pdf-climate/ucsb-full-report.pdf).

```{r, echo = FALSE}
#recreate data
df <- tribble(~response,
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "yes",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              "no",
              )

```


```{r}
# Create a function that will calculate the proportion of "yes" answers

prop_fun <- function (x,i) {sum(x[i]=="yes")/length(x[i])
  }


res <- df$response

# calculate the proportion of yes responses in 10000 bootstrap samples
resboot_10000 <- boot(res, 
                    statistic = prop_fun,
                    R = 10000)

resboot_10000
```

```{r}
# convert vector of bootstrap proportions into df
resboot_10000_df <- data.frame(bs_prop = resboot_10000$t)


# Histogram of 10000 bootstrap sample proportions:
ggplot(data = resboot_10000_df, aes(x = bs_prop)) +
  geom_histogram(bins=24)+
  labs(x="proportion yes responses")+
  theme_bw()
```

```{r}
# calculate bootstrap confidence interval
boot.ci(resboot_10000, conf = 0.95)
# 95 of 100 calculated confidence intervals will contain the actual population parameter

```
The mean proportion of UCSB community members identifying as nonbinary/genderqueer who responded that they had personally experienced “exclusionary, offensive, hostile or intimidating conduct” was 0.61 (22 out of 36 respondents), with a bootstrapped 95% confidence interval of [0.44, 0.78] (n = 10,000 bootstrap samples). 
