---
title: "task1"
author: "Logan Kozal"
date: "3/8/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(ggdendro)
```
## DATA & METADATA SOURCE: 
SBC LTER: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000
Creators: Santa Barbara Coastal LTER, & Melack, John M
Citation: Santa Barbara Coastal LTER and J. Melack. 2019. SBC LTER: Land: Stream chemistry in the Santa Barbara Coastal drainage area, ongoing since 2000 ver 16. Environmental Data Initiative. https://doi.org/10.6073/pasta/67a558a24ceed9a0a5bf5e46ab841174. 


## Read in data
### identify NAs, and get mean values per site
```{r}
stream <- read_csv(here::here("data","sbc_lter_registered_stream_chemistry.csv")) %>% 
  na_if(-999.0) 

stream_mean <- stream %>% 
  group_by(site_code) %>% 
  summarize(
    mean_nh4_uM = mean(na.omit(nh4_uM)),
    mean_no3_uM = mean(na.omit(no3_uM)),
    mean_po4_uM = mean(na.omit(po4_uM)),
    mean_tdn_uM = mean(na.omit(tdn_uM)),
    mean_tdp_uM = mean(na.omit(tdp_uM)),
    mean_tpc_uM = mean(na.omit(tpc_uM)),
    mean_tpn_uM = mean(na.omit(tpn_uM)),
    mean_tpp_uM = mean(na.omit(tpp_uM)),
    mean_tss_mgperLiter = mean(na.omit(tss_mgperLiter)),
    mean_spec_cond_uSpercm = mean(na.omit(spec_cond_uSpercm))
  )
```
## Calculate distance matrix
### remove sites with NAs, scale, and calculate euclidean distance
```{r}
#remove rows with NAs 
stream_nona <- stream_mean %>% 
  drop_na(c(2:11)) 

#scale (this might be unneccessary since most things are in the same units)
stream_scale <- stream_nona %>% 
  select(2:11) %>% 
  scale()

#add rownames back
rownames(stream_scale) <- stream_nona$site_code

# Calculate euclidean distance matrix
euc_dist <- dist(stream_scale, method = "euclidean")

```

## Clustering by the smallest maximum distance between two observations in distinct clusters - *complete linkage*
```{r}
# complete linkage hierarchical clustering
hc_complete <- hclust(euc_dist, method = "complete" )

# Plot dendrogram
ggdendrogram(hc_complete, 
             rotate = TRUE) +
  theme_minimal()+
  labs(x="Stream Site", "euclidean distance")
```

